PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-03-23 txt/manuscript.tex
Fix biblio

\bibitem{preskill} Preskill, J. "Quantum Computing in the NISQ era and beyond." Quantum 2 (2018): 79.

@@

	\bibitem{supermarq} Tomesh, T., Gokhale, P., Omole, V., Ravi, G. S., Smith, K. N., Viszlai, J., Wu, X.,  Hardavellas, N., Martonosi, M.R.,  Chong, F. T. (2022). Supermarq: A scalable quantum benchmark suite. In 2022 IEEE International Symposium on High-Performance Computer Architecture (HPCA) (pp. 587-603). IEEE.

@@

\bibitem{volume-in-practice} The web resource at\url{https://github.com/lanl/Quantum-Volume-in-Practice}. Accessed on 2023-02-18.

@@

\bibitem{puchala2018strategies} Puchała, Z.,  Pawela, Ł.,  Krawiec, A.,  Kukulski, R. "Strategies for
optimal single-shot discrimination of quantum measurements." Physical Review A

@@

\bibitem{helstrom1976quantum} Helstrom, C. W. (1969). "Quantum detection and estimation theory." Journal of Statistical Physics, 1(2), 231-252.

@@

\bibitem{hausdorff} Hausdorff, F. "Der wertvorrat einer bilinearform." Mathematische Zeitschrift 3.1 (1919): 314-316.
\bibitem{toeplitz} Toeplitz, O. "Das algebraische Analogon zu einem Satze von Fejér." Mathematische Zeitschrift 2.1 (1918): 187-197.

@@

and Raphael C. Pooser. "Generative model benchmarks for superconducting
qubits." Physical Review A 99.6 (2019).

>>>>

\bibitem{preskill} Preskill, J. Quantum Computing in the NISQ era and beyond. Quantum 2 (2018): 79.

@@

	\bibitem{supermarq} Tomesh, T., Gokhale, P., Omole, V., Ravi, G. S., Smith, K. N., Viszlai, J., Wu, X.,  Hardavellas, N., Martonosi, M.R.,  Chong, F. T. (2022). Supermarq: A scalable quantum benchmark suite. In 2022 IEEE International Symposium on High-Performance Computer Architecture (HPCA) 587-603. IEEE.

@@

\bibitem{volume-in-practice} The web resource at \url{https://github.com/lanl/Quantum-Volume-in-Practice}. Accessed on 2023-02-18.

@@

\bibitem{puchala2018strategies} Puchała, Z.,  Pawela, Ł.,  Krawiec, A.,  Kukulski, R. Strategies for
optimal single-shot discrimination of quantum measurements. Physical Review A

@@

\bibitem{helstrom1976quantum} Helstrom, C. W. (1969). Quantum detection and estimation theory. Journal of Statistical Physics, 1(2), 231-252.

@@

\bibitem{hausdorff} Hausdorff, F. (1919). Der wertvorrat einer bilinearform. Mathematische Zeitschrift, 3(1), 314-316.
\bibitem{toeplitz} Toeplitz, O. (1918). Das algebraische Analogon zu einem Satze von Fejér. Mathematische Zeitschrift, 2(1-2), 187-197.

@@

and Raphael C. Pooser. (2019). Generative model benchmarks for superconducting
qubits. Physical Review A 99(6), 062323.
